When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-03 06_Paper/COG-ED/Stage 2/Manuscript.Rmd

When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
The rmANOVA showed a significant difference between the SVs across $n$-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
All four pre-defined contrasts reached significance (Table\ \@ref(tab:H2a-contrasts)), so a purely linear contrast can be rejected.

@@

```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
kable(h2b_result.table,
        caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
        booktabs = T,                          # no vertical lines
        escape = F,                            # correctly print special characters)
        align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
             escape = F,                    # correctly print special characters
             threeparttable = T)            # line breaks in the footnote
```

@@

With another rmANOVA was used to investigate whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction.
Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large interindividual differences.

@@

The majority of participants (`r round(100*((nrow(data_SV[data_SV$level==1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ %) had an absolute preference for 1-back over the other levels, but that also means that there were `r round(100*((nrow(data_SV[data_SV$level!=1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ % who had an absolute preference for 2-, 3-, or 4-back, and `r round(100*((length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1])))/nrow(data_quest)), digits = 1)`\ % who preferred no specific level over all others.

>>>>

When asking participants what motivated their decisions in the effort discounting, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
**Figure XX in the Supplement** shows the different motivations in the context of the SVs per $n$-back level.

The rmANOVA showed a significant difference between the SVs across $n$-back levels (`r apa_print(hypothesis2a_rmanova)$full_result$level`, `r apa_print(hypothesis2a_BF)$statistic`).
All four pre-defined contrasts reached significance (Table\ \@ref(tab:H2a-contrasts)), so a purely linear contrast can be rejected.

@@

```{r H2b-results, echo=FALSE, message=FALSE, warning=FALSE}
kable(h2b_result.table,
        caption = "Results of the multi level model on the influence of n-back level (as a declining logistic contrast) and task performance on subjective values.",
        booktabs = T,                          # no vertical lines
        escape = F,                            # correctly print special characters)
        align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    footnote(general = "$SE$ = standard error, $df$ = degrees of freedom, $SD$ = standard deviation.",
             escape = F,                    # correctly print special characters
             threeparttable = T)            # line breaks in the footnote
```

@@

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction.
Post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large interindividual differences.

@@

The majority of participants (`r round(100*((nrow(data_SV[data_SV$level==1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ %) had an absolute preference for 1-back over the other levels, but that also means that there were `r round(100*((nrow(data_SV[data_SV$level!=1 & data_SV$sv==1,]))/nrow(data_quest)), digits = 1)`\ % who had an absolute preference for 2-, 3-, or 4-back, and `r round(100*((length(setdiff(unique(data_SV$subject), data_SV$subject[data_SV$sv == 1])))/nrow(data_quest)), digits = 1)`\ % who preferred no specific level over all others.
It shows that when given the choice, there is a large number of participants who do not prefer the easiest level, confirming the necessity of an effort discounting paradigm that works independent of the objective task load.
The CAD paradigm provides the means to depict these preferences.

Despite the visual separation of the SVs of participants with very low and high NFC scores in higher $n$-back levels, the NFC group did not reach significance in predicting SVs.
This was likely due to the bandwidth of SVs of participants with NFC scores around the median, and due to the fact that the difference appeared most pronounced for $4$-back, and we only analyzed the difference scores between 1- and 2-back and 2- and 3-back.
The analysis of NASA-TLX scores showed that the sum score increased with every $n$-back level, and that participants with NFC scores below the median had higher NASA-TLX scores for 3- and 4-back than those below the median.
This demonstrates that higher $n$-back levels have a higher discriminatory power regarding interindividual differences in subjective effort perception.
This was also supported by the fact that higher $n$-back levels were perceived as more aversive, and participants with NFC scores below the median reported higher aversion than those with NFC scores above the median.
